Explore immune cell types in Ewing sarcoma

### 2025-03-20 analyses/infercnv-consensus-cell-type/exploratory-notebooks/01_ewings-consensus-cell-types.Rmd
notebook updates and re-render

* There are sufficient immune cells to pool together to run `inferCNV` specifying them as a normal reference
* We could also consider using only `macrophage` cells, or combined `macrophage` and all `T cell` types together, if we wanted to assess any potential effect of limit the types of immune cells feeding into `inferCNV`. 
* There are 17 cells which are annotated as an immune consensus cell type (specifically, macrophage and mature T cell) which the `cell-type-ewings` module annotated as tumor cells.
We would probably want to exclude these cells from any normal reference.

>>>>

* There are sufficient immune cells to pool together to run `inferCNV` specifying them as a normal reference
* We could also consider combined `macrophage` and all `T cell` types together to assess any potential effect of limiting the types of immune cells feeding into `inferCNV`
* We should exclude library `SCPCL001111` from analysis since it has less than 100 cells.  
* There are 17 cells which are annotated as an immune consensus cell type (specifically, macrophage and mature T cell) which the `cell-type-ewings` module annotated as tumor cells.
We would probably want to exclude these cells from any normal reference.
